A new breeding crossover approach for evolutionary algorithms

### 2023-09-21 paper.tex
Functions F1 to F12 update.

    \begin{itemize}
        \item In function F1 for the ten-dimensional category, the Continuous Range Crossover (CRx) methodology outperformed the One Point Crossover (OPx) methodology in the statistical test. We needed to find more evidence for the thirty dimensions category to determine whether any crossover alternative would be better.
        \item At function F2 for the category of 10 dimensions, again, the CRx strategy outperformed the alternative approach OPx in the statistical test. More evidence was required for the thirty dimensions category to declare any of them as the best.
        \item At function F3 for both categories, 10 and 30 dimensions, the statistical test found better results for our proposed CRx strategy than the alternative OPx.
        \item At function F4, only for the 10-dimensional category, the CRx strategy proved to be better through the statistical test, while for the 30-dimensional variety, it could not identify any of them as the best.
        \item At function F5, only for the 10-dimensional category, the proposed strategy CRx passed the statistical test to its alternative OPx, while for the 30-dimensional type, they obtained similar results.
    \end{itemize}

@@

>>>>

    \begin{itemize}
        \item In function F1 for the ten-dimensional category, the Continuous Range Crossover (CRx) methodology outperformed the One Point Crossover (OPx) methodology in the statistical test. We needed to find more evidence for the thirty dimensions category to determine whether any crossover alternative would be better.
        \item At function F2 for the category of 10 dimensions, again, the CRx strategy outperformed the alternative approach OPx in the statistical test. More evidence was required for the thirty dimensions category to declare any of them as the best.
        \item At function F3 for both categories, 10 and 30 dimensions, the statistical test found better results for our proposed CRx strategy than the alternative OPx.
        \item At function F4, only for the 10-dimensional category, the CRx strategy proved to be better through the statistical test, while for the 30-dimensional variety, it could not identify any of them as the best.
        \item At function F5, only for the 10-dimensional category, the proposed strategy CRx passed the statistical test compared to its alternative OPx, while for the 30-dimensional type, they obtained similar results.
    \end{itemize}

@@

    We describe the results shown in Figure~\ref{fig.experiment_F11-F15}, including functions F11 through F15.

    \begin{itemize}
        \item At function F11, only for the 10-dimensional category, the original OPx passed the statistical test compared to our proposed strategy CRx, while for the 30-dimensional type, they obtained similar results.
        \item At function F12, for both categories, 10 and 30 dimensions, the CRx strategy found better results than the OPx alternative, passing the statistical test in both cases.

    \end{itemize}
